Algorithms for the Automated Correction of Vertical Drift in Eye-Tracking Data

### 2021-04-03 manuscript/manuscript.tex
Update publication status and doi
Update project title

\title{Algorithms for the Automated Correction of Vertical Drift in Eye Tracking Data}

@@

\authornote{\textbf{Cite as:} Carr, J.\@ W., Pescuma, V.\@ N., Furlan, M., Ktori, M., \& Crepaldi, D.\@ (under review). Algorithms for the automated correction of vertical drift in eye tracking data. https://doi.org/10.31219/osf.io/jg3nc}

>>>>

\title{Algorithms for the Automated Correction of Vertical Drift in Eye-Tracking Data}

@@

\authornote{\textbf{Cite as:} Carr, J.\@ W., Pescuma, V.\@ N., Furlan, M., Ktori, M., \& Crepaldi, D.\@ (2021). Algorithms for the automated correction of vertical drift in eye-tracking data. \textit{Behavior Research Methods}. https://doi.org/10.3758/s13428-021-01554-0}
